Timeliness of security updates for Android

### 2015-03-25 securityupdates.tex
Comment out paragraph on vulnerability distribution to save space

The discovery dates of our vulnerabilities are not uniform. 
In particular the data shows a large gap from 2011-10-06 to 2013-02-18 where we do not know of any discoveries of critical vulnerabilities affecting all Android devices.
The cause of this quiet period is unclear.
Possible explanations are that: (i) most devices were exposed to known vulnerabilities so there was reason to look for new ones;
(ii) device manufacturers made it easier to install custom versions of Android, reducing the need for users to root their devices; and
(iii) device manufacturer specific vulnerabilities (which are not in our analysis here) were easier to find and so attackers looking for vulnerabilities adjusted their focus.
\todolater{If we need to save space then delete this paragraph}

>>>>

%The discovery dates of our vulnerabilities are not uniform. 
%In particular the data shows a large gap from 2011-10-06 to 2013-02-18 where we do not know of any discoveries of critical vulnerabilities affecting all Android devices.
%The cause of this quiet period is unclear.
%Possible explanations are that: (i) most devices were exposed to known vulnerabilities so there was reason to look for new ones;
%(ii) device manufacturers made it easier to install custom versions of Android, reducing the need for users to root their devices; and
%(iii) device manufacturer specific vulnerabilities (which are not in our analysis here) were easier to find and so attackers looking for vulnerabilities adjusted their focus.
